---
title: "p8105_hw6_jdr2191"
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r import_data}
birthweight_df = 
  read_csv("birthweight.csv") %>%
  mutate(babysex = factor(babysex, levels = c(1,2))) %>%
  mutate(frace = factor(frace, levels = c(1,2,3,4,8,9))) %>%
  mutate(malform = factor(malform, levels = c(0,1))) %>%
  mutate(mrace = factor(mrace, levels = c(1,2,3,4,8)))
```

Propose a regression model for birthweight. 

First I am going to investigate the data we have to determine which variables might be appropriate for inclusion. 
```{r}
unique(pull(birthweight_df, pnumlbw))
unique(pull(birthweight_df, pnumsga))
```
* All values of pnumlbw (previous number of low birth weight babies) are 0. Will not be an informative variable for inclusion in the model. 

* All values of pnumsga (number of prior small for gestational age babies) are 0. Will not be an informative variable for inclusion in the model. 

At my first pass at a model, I will include variables that I think are most appropriate. 
```{r model0}
model0 = lm(bwt ~ delwt + frace + mrace + smoken + gaweeks + ppbmi + momage + 
                  wtgain + malform, data = birthweight_df)

summary(model0)
```
Based on these results, it looks like frace, momage and malform are not significant predictors of bwt. I will remove these variables from the next iteration of the model. I will also add additional variables that may be appropriate. 

```{r model1}
model1 = lm(bwt ~ delwt + mrace + smoken + gaweeks + ppbmi + babysex + bhead + blength + 
                  parity, data = birthweight_df)

summary(model1)

model1 %>%
  broom::tidy()
```
Compare your model to two others:

* One using length at birth and gestational age as predictors (main effects only)

* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r comparison_models}
model2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
model3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex +
                  blength * babysex + bhead * blength * babysex, data = birthweight_df)
```

