---
title: "p8105_hw6_jdr2191"
output: github_document
---

```{r load_libraries, message=FALSE}
library(tidyverse)
library(purrr)
library(modelr)
library(viridis)
```

## Problem 1

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r import_bwt_data, message=FALSE}
birthweight_df = 
  read_csv("birthweight.csv") %>%
  mutate(babysex = factor(babysex, levels = c(1,2))) %>%
  mutate(frace = factor(frace, levels = c(1,2,3,4,8,9))) %>%
  mutate(malform = factor(malform, levels = c(0,1))) %>%
  mutate(mrace = factor(mrace, levels = c(1,2,3,4,8)))
```

Propose a regression model for birthweight. 

First I am going to investigate the data we have to determine which variables might be appropriate for inclusion. 
```{r investigate_bwt, message=FALSE}
unique(pull(birthweight_df, pnumlbw))
unique(pull(birthweight_df, pnumsga))
```
* All values of pnumlbw (previous number of low birth weight babies) are 0. Will not be an informative variable for inclusion in the model. 

* All values of pnumsga (number of prior small for gestational age babies) are 0. Will not be an informative variable for inclusion in the model. 

At my first pass at a model, I will include variables that I think are most appropriate. 

```{r model0, message=FALSE}
model0 = lm(bwt ~ delwt + frace + mrace + smoken + gaweeks + ppbmi + momage + 
                  wtgain + malform, data = birthweight_df)

summary(model0)
```
Based on these results, it looks like frace, momage and malform are not significant predictors of bwt. I will remove these variables from the next iteration of the model. I will also add additional variables that may be appropriate. 

```{r model1, message=FALSE}
model1 = lm(bwt ~ delwt + mrace + smoken + gaweeks + ppbmi + babysex + bhead + blength + 
                  parity, data = birthweight_df)

summary(model1)

model1 %>%
  broom::tidy()
```

Diagnostics
```{r model_diagnostics, message=FALSE}
modelr::add_residuals(birthweight_df, model1)

modelr::add_predictions(birthweight_df, model1)

birthweight_df %>%
  modelr::add_residuals(model1) %>%
  modelr::add_predictions(model1) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(color = "#21A8BD") +
  labs(x = "Fitted Values", y = "Residuals") + 
  ggtitle("Plot of model residuals against fitted values") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) 
```

Compare your model to two others:

* One using length at birth and gestational age as predictors (main effects only)

* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r comparison_models, message=FALSE}
model2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
model3 = lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex +
                  blength * babysex + bhead * blength * babysex, data = birthweight_df)
```

Make this comparison in terms of the cross-validated prediction error
```{r model_cv, message=FALSE}
cv_df =
  crossv_mc(birthweight_df, 50) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df2 = 
cv_df %>%
  mutate(
    model1 = map(train, ~lm(bwt ~ delwt + mrace + smoken + gaweeks + 
                                  ppbmi + babysex + bhead + blength + parity, data = .x)), 
    model2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)), 
    model3 = map(train, ~lm(bwt ~ bhead + blength * babysex * bhead, data = .x))
  ) %>%
  mutate(
    rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)), 
    rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
    rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y))
  )
```

Look at output
```{r cv_investigation, message=FALSE}
cv_df2 %>% 
  select(
    starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
    ggplot(aes(x = model, y = rmse, fill = model)) +
    geom_boxplot() +
    scale_fill_viridis_d(option = "D") +
    labs(x = "Model", y = "RMSE", col = "Model") +
    ggtitle("RMSE Plots for All Models") +
    theme_minimal() +
    theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
```

## Problem 2

Importing weather dataset. 
```{r import_weather_df, message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Boostrapping weather dataset. 
```{r bootstrap_weather_df, message=FALSE}
weather_df2 =
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    glance = map(models, broom::glance),
    results = map(models, broom::tidy)) %>%
  unnest(results) %>%
  unnest(glance, names_repair = "universal") %>%
  select(strap, .id, models, r.squared, term, estimate)

weather_df3 = 
  weather_df2 %>%
  mutate(term = if_else(term != "tmin", "Intercept", "tmin"))

wide_weather_df = 
  weather_df3 %>%
  select(term, estimate, .id, r.squared) %>%
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) 

weather_df4 = 
wide_weather_df %>%
  mutate(logb0b1 = log(Intercept)*log(tmin)) %>%
  select(.id, r.squared, logb0b1) 
```

Generate plots of R squared and Log(beta0 * beta1)
```{r weather_df_plots, message=FALSE}
weather_df4 %>%
  ggplot(aes(x = r.squared)) + 
  geom_density(color = "#6D58B0", size = 1) +
  labs(x = "R Squared", y = "Density") +
  ggtitle("Distribution of R Squared Values for 5,000 Bootstrap Samples") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) 

weather_df4 %>%
  ggplot(aes(x = logb0b1)) + 
  geom_density(color = "#6D58B0", size = 1) +
  labs(x = "Log (Beta 0 * Beta 1)", y = "Density") +
  ggtitle("Distribution of Log(Beta 0 * Beta 1) for 5,000 Bootstrap Samples") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) 
```

Identify the 2.5% and 97.5% quantiles to provide 95% confidence intervals for R squared and Log (Beta 0 * Beta 1)

```{r 95%_CIs, message=FALSE}
weather_df5 = 
  weather_df4 %>%
  select(r.squared, logb0b1)

sapply(weather_df5, function(x) quantile(x, probs = c(0.025, 0.975))) %>%
  knitr::kable()
```


